---
title: "Data 607 Assignment 6"
author: "Sung Lee"
date: "3/14/2020"
output: 
  html_document: 
    df_print: paged
    toc: true
    toc_float: true
    toc_collapsed: true
    toc_depth: 3
theme: yeti
---

[Assignment on RPubs](https://rpubs.com/logicalschema/data607_week6 "Sung's Week 6 Assignment Rpubs")
<br>
[Rmd on Github](https://github.com/logicalschema/DATA607/blob/master/week6/SungLee-Week6.Rmd "Sung's Week 5 Assignment Github")




# Introduction

This week's assignment is to work with the web uibiquitous forms of `html`, `xml`, and `json`. This assignment will work with and identify differences between three files: `books.html`, `books.xml`, and `books.json`. The books in the brief inventory are from the dystopian science fiction genre. One book *Looking Backward: 2000-1887* by Edward Bellamy has another author Sylvester Baxter writing an introduction. Each book entry has the fields: `Title`, `Authors`, `ISBN-13`, and `Pages`. 


# Import {.tabset}

Let's import the formats into R. Each tab will have the code on how to import the various formats.

Let's setup the libraries we will use with the following code.

```{r}
library(xml2)
library(rvest)  # This is a handy Tidyverse library for HTML parsing
library(rjson)

```


## HTML


```{r}


```


## XML
```{r}


```

## JSON
```{r}


```