---
title: "Data 607 Week 9"
author: "Sung Lee"
date: "3/24/2020"
output: 
  html_document:
    code_folding: show
    df_print: paged
    toc: true
    toc_float: true
    toc_collapsed: true
    smooth_scroll: false
    toc_depth: 3
number_sections: true
theme: paper
---

[Assignment on RPubs](https://rpubs.com/logicalschema/data607_week9 "Sung's Week 9 Assignment Rpubs")
<br>
[Rmd on Github](https://github.com/logicalschema/DATA607/blob/master/week9/SungLee-Week9.Rmd
 "Sung's Week 9 Assignment Github")


# Introduction

This asignment will employ the New York Times' set of APIs to read data into JSON and transform it into an R data frame. We will use the New York Times Top Stories API and select world stories. An example of the call would use this API call `https://api.nytimes.com/svc/topstories/v2/world.json?api-key=yourkey`.

# Import

Let's import the data from the New York Times. 

```{r}
library(jsonlite)


# Call the JSON frm the NY Times by constructing the call store
apikey <- "WVJoOYFhRCJAX5qahIguxfbZmmcpVeBA"
baseurl <- "https://api.nytimes.com/svc/topstories/v2/world.json?api-key="

url <- URLencode(paste0(baseurl, apikey))
request <- fromJSON(url)
stories <- request$results

```

<br>
This is how the the top world stories looks using the `fromJSON` function from the `jsonlite` package.

```{r}
stories
```

Let's look at particular aspects of the data frame.

```{r}

# These are the column names
colnames(stories)

# This is the data type of the object
class(stories)

# Let's look at the first 10 titles 
stories[1:10, 3:5]

```

<br>
Let's look at how many of the top stories have Coronavirus in their title.

```{r}
library(stringr)
library(dplyr)

coronavirus <- stories %>% 
  filter(str_detect(title, "Coronavirus"))

cNumber <- nrow(coronavirus)

```

There are **`r cNumber`** stories in the top stories with `Coronavirus` in their title.

<br>
<br>

# Conclusion

`jsonlite` is a welcome package for working with APIs that generate JSON objects for data. 








