---
title: "Sung Lee Project 1"
author: "Sung Lee"
date: "2/13/2020"
output: 
 html_document: 
  df_print: paged
---

[Project on RPubs](https://rpubs.com/logicalschema/data607_project1 "Sung's Project 1 Assignment Rpubs")
<br>
[Rmd on Github](https://github.com/logicalschema/DATA607/blob/master/Project%201/Sung%20Lee%20Project%201.Rmd "Sung's Project 1 Assignment Github")


## Introduction  
This project will read the Chess tournament text file hosted on Github at https://raw.githubusercontent.com/logicalschema/DATA607/master/Project%201/tournamentinfo.txt and will generate a CSV file. We will only be interested in the player's wins, losses, and draws with other opponents. 

The following format will be the CSV file that will be exported:


Player's Name | Player's State | Total Number of Points | Player's Pre-Rating | Average Pre-Chess Rating of Opponents
--------------|----------------|------------------------|---------------------|---------------------------------------
Gary Hua      | ON             | 6.0                    | 1794                | 1605

I will add other columns named player's ID, player's number of games, and player's opponents. These are for internal purposes.

```{r}
library(stringr)

options(warn=-1) # Turning off warnings with reading the text file

textFile <- readLines("https://raw.githubusercontent.com/logicalschema/DATA607/master/Project%201/tournamentinfo.txt")
options(warn=0) # Turning warnings back on

head(textFile, 13)

#Create internal dataframe
playerData <- data.frame(matrix(ncol = 7, nrow = 0))
names(playerData) <- c("ID", "Name", "State", "totalPoints" ,"preRating", "NumberofGames", "Opponents")



i <- 5  # Skipping the header rows and lines that have --------------------
while (i <= length(textFile)) {
  row1 <- unlist(strsplit(textFile[i], split='|', fixed=TRUE))
  row2 <- unlist(strsplit(textFile[i + 1],  split ='|', fixed=TRUE))
  
  #Get the player's id
  playerID <- as.numeric(str_trim(row1[1]))

  #Get the player's name
  playerName <- str_trim(row1[2])

  #Get the player's state
  playerState <- str_trim(row2[1])

  #Get the player's total number of points
  playertotalPoints <- as.numeric(str_trim(row1[3]))

  #Get the player's pre-rating
  playerpreRating <- str_match(str_trim(row2[2]), "R:(.*?)->")[,2]    #Grab the text between R: and the ->
  playerpreRating <- as.numeric(str_remove(str_trim(playerpreRating), 'P(.*)$')) #Remove non-numeric characters

  #Get the player's number of games played in the tournament: counting only wins, losses, and draws
  #Also, get the player's opponents
  playerNumberofGames <- 0
  playerOpponents <- vector()

  for (j in 4:10) {
   rowValue <- row1[j]
   if ( grepl('W', rowValue) || grepl('L', rowValue) || grepl('D', rowValue)) {
     playerNumberofGames <- playerNumberofGames + 1
   }
   
   #playerOpponents <- paste(playerOpponents, str_match(rowValue, '\\d+'), sep = ",")
   playerOpponents <- c(playerOpponents, as.numeric(str_match(rowValue, '\\d+')))
  }

  #playerOpponents <- str_remove(playerOpponents, '^,') #Remove leading ,
  

  #"ID", "Name", "State", "totalPoints" ,"preRating", "NumberofGames", "Opponents"
  
  newRow <- data.frame(playerID, playerName, playerState, playertotalPoints, playerpreRating, playerNumberofGames, playerOpponents)
  playerData <- rbind(playerData, newRow)
  
  i <- i + 3
}

head(playerData, 10)

```

---
title: "Sung Lee Project 1"
author: "Sung Lee"
date: "2/13/2020"
output: 
 html_document: 
  df_print: paged
---

[Project on RPubs](https://rpubs.com/logicalschema/data607_project1 "Sung's Project 1 Assignment Rpubs")
<br>
[Rmd on Github](https://github.com/logicalschema/DATA607/blob/master/Project%201/Sung%20Lee%20Project%201.Rmd "Sung's Project 1 Assignment Github")


## Introduction  
This project will read the Chess tournament text file hosted on Github at https://raw.githubusercontent.com/logicalschema/DATA607/master/Project%201/tournamentinfo.txt and will generate a CSV file. We will only be interested in the player's wins, losses, and draws with other opponents. 

The following format will be the CSV file that will be exported:


Player's Name | Player's State | Total Number of Points | Player's Pre-Rating | Average Pre-Chess Rating of Opponents
--------------|----------------|------------------------|---------------------|---------------------------------------
Gary Hua      | ON             | 6.0                    | 1794                | 1605

I will add other columns named player's ID, player's number of games, and player's opponents. These are for internal purposes.

```{r}
library(stringr)

options(warn=-1) # Turning off warnings with reading the text file

textFile <- readLines("https://raw.githubusercontent.com/logicalschema/DATA607/master/Project%201/tournamentinfo.txt")
options(warn=0) # Turning warnings back on

head(textFile, 13)

#Create internal dataframe
playerData <- data.frame(matrix(ncol = 7, nrow = 0))
playerInfo <- c("ID", "Name", "State", "totalPoints" ,"preRating", "NumberofGames", "Opponents")
colnames(playerData) <- playerInfo



i <- 5  # Skipping the header rows and lines that have --------------------
while (i <= length(textFile)) {
  row1 <- unlist(strsplit(textFile[i], split='|', fixed=TRUE))
  row2 <- unlist(strsplit(textFile[i + 1],  split ='|', fixed=TRUE))
  
  #Get the player's id
  playerID <- as.numeric(str_trim(row1[1]))

  #Get the player's name
  playerName <- str_trim(row1[2])

  #Get the player's state
  playerState <- str_trim(row2[1])

  #Get the player's total number of points
  playertotalPoints <- as.numeric(str_trim(row1[3]))

  #Get the player's pre-rating
  playerpreRating <- str_match(str_trim(row2[2]), "R:(.*?)->")[,2]    #Grab the text between R: and the ->
  playerpreRating <- as.numeric(str_remove(str_trim(playerpreRating), 'P(.*)$')) #Remove non-numeric characters

  #Get the player's number of games played in the tournament: counting only wins, losses, and draws
  #Also, get the player's opponents
  playerNumberofGames <- 0
  playerOpponents <- ""

  for (j in 4:10) {
   rowValue <- row1[j]
   if ( grepl('W', rowValue) || grepl('L', rowValue) || grepl('D', rowValue)) {
     playerNumberofGames <- playerNumberofGames + 1
   }
   
   playerOpponents <- paste(playerOpponents, str_match(rowValue, '\\d+'), sep = ",")
  }

  playerOpponents <- str_remove(playerOpponents, '^,') #Remove leading ,

  
#  playerData ("ID", "Name", "State", "totalPoints" ,"preRating", "NumberofGames", "Opponents")
  
  
  newRow <- data.frame(playerID, playerName, playerState, playertotalPoints, playerpreRating, playerNumberofGames, playerOpponents)
  playerData <- rbind(playerData, newRow)
  
  #playerData
  
  i <- i + 3
}

head(playerData, 10)

```
## Average Pre-chess Rating of Opponents

With the player information dataframe created. Next, I will create the column average pre-chess rating of opponents for each player.

```{r}

#playerData ("playerID", "playerName", "playerState", "playertotalPoints" ,"playerpreRating", "playerNumberofGames", "playerOpponents")
colnames(playerData)
nrow(playerData)

for (i in 1:nrow(playerData)) {
    row <- playerData[i,]
    sum <- 0
    
#    opponents <- row[7]
#    for (value in opponents) {
#       if (is.na(value) == FALSE) {
#         sum <- sum + playerData[which(playerData$playerID == value), 5]
#       }
#    }
    
#    print(sum / row[6])
}

```

