---
title: "Week 3 Assignment"
author: "Sung Lee"
date: "2/12/2020"
output: 
  html_document: 
    df_print: paged
---

[Assignment on RPubs](https://rpubs.com/logicalschema/data607_week3 "Sung's Week 2 Assignment Rpubs")
<br>
[Rmd on Github](https://github.com/logicalschema/DATA607/blob/master/week3/Sung%20Lee%20Assignment%203.Rmd "Sung's Week 3 Assignment Github")

1. Using the 173 majors listed in fivethirtyeight.com’s College Majors dataset [https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/], provide code that identifies the majors that contain either "DATA" or "STATISTICS"  

```{r, question1}
 library(stringr)

 majorCSV <- read.csv("https://raw.githubusercontent.com/logicalschema/DATA607/master/week3/majors-list.csv")


 #The following code uses a regular expression DATA or STATISTICS and searches through the Major field of the data.
 grep('DATA|STATISTICS', majorCSV$Major,  value = TRUE)

```
<br>

2. Write code that transforms the data below:  

```{r, eval=FALSE}
[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"

[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  

[9] "elderberry"   "lime"         "lychee"       "mulberry"    

[13] "olive"        "salal berry"
```

Into a format like this:

```{r, eval=FALSE}
c("bell pepper", "bilberry", "blackberry", "blood orange", "blueberry", "cantaloupe", "chili pepper", "cloudberry", "elderberry", "lime", "lychee", "mulberry", "olive", "salal berry")
```
<br>

```{r, question2}
w <- c("bell pepper","bilberry","blackberry","blood orange")
x <- c("blueberry","cantaloupe","chili pepper","cloudberry") 
y <- c("elderberry","lime","lychee","mulberry") 
z <- c("olive","salal berry")


combined <- c(w, x, y, z)

print(combined)

```
<br>

### The two exercises below are taken from R for Data Science, 14.3.5.1 in the on-line version:  

3. Describe, in words, what these expressions will match:

    (.)\1\1
    "(.)(.)\\2\\1"
    (..)\1
    "(.).\\1.\\1"
    "(.)(.)(.).*\\3\\2\\1"  
    
    





