---
title: "Week 3 Assignment"
author: "Sung Lee"
date: "2/12/2020"
output: 
  html_document: 
    df_print: paged
---

[Assignment on RPubs](https://rpubs.com/logicalschema/data607_week3 "Sung's Week 2 Assignment Rpubs")
<br>
[Rmd on Github](https://github.com/logicalschema/DATA607/blob/master/week3/Sung%20Lee%20Assignment%203.Rmd "Sung's Week 3 Assignment Github")

1. Using the 173 majors listed in fivethirtyeight.com’s College Majors dataset [https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/], provide code that identifies the majors that contain either "DATA" or "STATISTICS"  

    ```{r, question1}
     library(stringr)

     majorCSV <- read.csv("https://raw.githubusercontent.com/logicalschema/DATA607/master/week3/majors-list.csv")


     #The following code uses a regular expression DATA or STATISTICS and searches through the Major field of the data.
    grep('DATA|STATISTICS', majorCSV$Major,  value = TRUE)

    ```
<br>

2. Write code that transforms the data below:  

    ```{r, eval=FALSE}
    [1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"

    [5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  

    [9] "elderberry"   "lime"         "lychee"       "mulberry"    

    [13] "olive"        "salal berry"
    ```

    Into a format like this:

    ```{r, eval=FALSE}
    c("bell pepper", "bilberry", "blackberry", "blood orange", "blueberry", "cantaloupe", "chili pepper", "cloudberry", "elderberry", "lime", "lychee", "mulberry", "olive", "salal berry")
    ```
    
    <br>

    ```{r, question2}
    w <- c("bell pepper","bilberry","blackberry","blood orange")
    x <- c("blueberry","cantaloupe","chili pepper","cloudberry") 
    y <- c("elderberry","lime","lychee","mulberry") 
    z <- c("olive","salal berry")


    combined <- c(w, x, y, z)

    print(combined)

    ```
    
<br>

#### The two exercises below are taken from R for Data Science, 14.3.5.1 in the on-line version:  

3. Describe, in words, what these expressions will match:

    **(.)\1\1**  
    This expression matches on characters, except line breaks, that is followed by a "\1\1". Examples would be "b\1\1", "c\1\1", or "5\1\1".   

    ```{r}
    x <- c("b\1\1", "c\1\1", "hello\1\1", "yellow")
    str_match(x, '(.)\1\1')  
    ```
    
    
    **"(.)(.)\\2\\1"**  
    This expression matches strings that contain pairs of characters, excluding line breaks, that are followed by a reverse of their order. Examples would be "abba", "0101", or "daad".  
    
    ```{r}
    x <- c("abba", "0110", "ACTGGTCA", "yellow")
    str_match(x, "(.)(.)\\2\\1")  
    ```
    
    **(..)\1**  
    This expression matches strings that have a couple of characters, excluding line breaks, that are followed by a "\1". Examples would be "ab\1", "54\1", or "11\1".  
    
    ```{r}
    x <- c("ab\1", "red", "A\1", "AABBCC\1")
    str_match(x, '(..)\1')  
    ```    
    
    
    **"(.).\\1.\\1"**
    This expression matches strings that contain a character that repeats in the 2 and 4 places over from its first occurrence. Examples would be "a0a1a", "c1d1e1", and "-1-2-3". 
    
    ```{r}
    x <- c("a0a1a", "blue", "c1d1e1", "-1-2-3")
    str_match(x, "(.).\\1.\\1")
    ```    
        
    
    **(.)(.)(.).*\\3\\2\\1**
    This expression matches any sequence of strings that are encapsulated by 3 characters, excluding line breaks, where the end string is a reverse order of those 3 characters. Examples would be "abcjfkdjkfjicba", "0110Middleofthestring110".
    
    ```{r}
    x <- c("abcjfkdjkfjicba", "redyellow001middle100kdlskdls", "beginbegin1middlegebend", "98&^A")
    str_match(x, "(.)(.)(.).*\\3\\2\\1")  #Note the \ needs to be escaped in the expression.
    
    ```

<br>

4. Construct regular expressions to match words that  

    Start and end with the same character:  
    "^(.)(.*)\\1$"

    ```{r}
    x <- c("amiddleofthestringa", "0red,yellow,green0", "red", "9*&^(^Hjshjshf9")
    str_match(x, "^(.)(.*)\\1$")  #Note the \ needs to be escaped in the expression.
    
    ```
    
    Contain a repeated pair of letters (e.g. "church" contains "ch" repeated twice.):  
    "(..)(.*)\\1"
    
    ```{r}
    x <- c("church", "blue", "red", "abracadabra")
    str_match(x, "(..)(.*)\\1")  #Note the \ needs to be escaped in the expression.
    
    ```
    
    Contain one letter repeated in at least three places (e.g. "eleven" contains three "e"s.)  
    "(.)(.*)\\1(.*)\\1"
    
    ```{r}
    x <- c("eleven", "blue", "010001001010", "yellow submarine light")
    str_match(x, "(.)(.*)\\1(.*)\\1")  #Note the \ needs to be escaped in the expression.
    
    ```    
    
    







